Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-25 paper.tex
Added positive ratio of the untility metrices

Figure~\ref{fig:pre-freesurfer-5-7} shows the difference matrix
obtained for the PreFreesurfer pipeline\todo{Remove title from figure,
  remove color scale, add axes labels.}. The computational
reproducibility of the PreFreesurfer pipeline varies across subjects,
which motivates our study. Nevertheless, some files behave
consistently across all subjects, leading to complete black or white
lines. The ratio of positive elements in this matrix is
\todo{x}\%. Similar matrices were obtained with this pipeline for
CentOS~6 vs CentOS~7 and for CentOS~5 vs CentOS~6, see
Figures~\ref{fig:pre-freesurfer-5-6} and~\ref{fig:pre-freesurfer-5-7}.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\linewidth}
	\includegraphics[width=\columnwidth]{figures/utility_5vs6_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS6}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
	 \includegraphics[width=\columnwidth]{figures/utility_5vs7_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS7}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
	\includegraphics[width=\columnwidth]{figures/utility_6vs7_PFS}
  \caption{Utility matrix of CentOS6 vs CentOS7}
  \label{fig:utility metrics}
  \end{subfigure}
\end{figure}

>>>>

Figure~\ref{fig:utility metrices} shows the difference matrices
obtained for the PreFreesurfer pipeline. The computational
reproducibility of the PreFreesurfer pipeline varies across subjects,
which motivates our study. Nevertheless, some files behave
consistently across all subjects, leading to complete black or white
lines. The ratio of positive elements in utility matrix of CentOS5 vs CentOS6(C5C6),  CentOS5 vs CentOS7(C5C7) and  CentOS6 vs CentOS7(C6C7) are
$0.34$, $0.79$ and $0.79$ respectively.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\linewidth}
	\includegraphics[width=\columnwidth]{figures/utility_5vs6_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS6}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
	 \includegraphics[width=\columnwidth]{figures/utility_5vs7_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS7}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
	\includegraphics[width=\columnwidth]{figures/utility_6vs7_PFS}
  \caption{Utility matrix of CentOS6 vs CentOS7}
  \label{fig:utility metrices}
  \end{subfigure}
\end{figure}
